              
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%   NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Joshua Taylor Eppinette} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{1080 West Peachtree St Nw Unit 1606} % Your address
\moveleft.5\hoffset\centerline{Atlanta, Georgia 30309}
\moveleft.5\hoffset\centerline{(770) 401-6678}
\moveleft.5\hoffset\centerline{josheppinette@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%   OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{OBJECTIVE}  

To obtain a career that will allow myself to take full advantage of my passion and experience in software engineering and computer science. 

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Bachelor of Computer Science,}  \hfill August 2012 - June 2015 \\
Southern Polytechnic State University, Marietta, GA\\
 
%----------------------------------------------------------------------------------------
%   Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS} 

{\sl Programming Languages:} Golang, Lua, Python, Java, C\#, JavaScript, C, C++. \\
{\sl Web Backend Technologies:} Nginx, NodeJS, Django, Tornado, Cassandra, Mongo, PostgreSQL, MySQL, Mandrill, AWS, Heroku. \\
{\sl Web Frontend Technologies:} AngularJS, JQuery, JQueryMobile, Bootstrap3, Firebase. \\
{\sl Software Engineering:} Agile, Continuous Integration, Scrum, Version control, Requirements analysis. \\
{\sl Software:} Atlassian Suite, Vagrant, Git, Vim, VirtualEnv, VirtualBox, Ansible, Gulp, NPM, Bower. \\
 
%----------------------------------------------------------------------------------------
%   PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Software Engineer} \hfill June 2015 - Present \\
Ionic Security Inc, Atlanta, GA
\begin{itemize}
\item Deployed standardization techniques throughout a large codebase.
\item Developed and designed a large AngularJS web application.
\item Leveraged Golang's compiled nature to simplify deployments and decrease ops issues.
\item Developed and maintained the development environment used by front end software engineers.
\item Developed a distributed authentication and routing system for a SOA using Golang, Nginx, and Lua.
\item Integrated the Jenkins Continuous Integration(CI) systems into the existing deployment processes.
\item Implemented web application security standards defined by OWASP.
\end{itemize} 

{\sl Software Engineer} \hfill August 2013 - June 2015 \\
Georgia Tech Research Institute, Electronic Systems Laboratory, Atlanta, GA 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed and developed Django/AngularJS software systems for the Department of Defense, Army, and Navy.
\item Presented software demos to Department of Defense derived clients.
\end{itemize}
 
{\sl Independent Software Contractor} \hfill May 2014 - February 2016\\
JTE Technologies, Atlanta, GA
\begin{itemize} 
\item Performed the full software development process with the end result of deploying a large scale software system that manages access to high priority physical and logical assets.
\item Designed the architecture for a Django/AngularJS software system.
\end{itemize} 


%----------------------------------------------------------------------------------------
%   COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 

\section{COMMUNITY \\ SERVICE}

Kennesaw Mountain Trail Club, {\sl Volunteer} \hfill February 2014 - Present \\
Race Against Violence, {\sl Volunteer} \hfill October 2012 - Present \\
9\/11 Memorial Stair Climb For The Fallen Heroes, {\sl Volunteer \& Climber} \hfill September 2016 - Present \\

%----------------------------------------------------------------------------------------
%   EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

Kappa Sigma Fraternity, {\sl President} \hfill August 2014 - May 2015\\
Kappa Sigma Fraternity, {\sl Treasurer} \hfill December 2013 - August 2014 \\
Technology Student Association, {\sl Team Leader} \hfill August 2011 - May 2012 \\
 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
              
            